% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Sergio Escoto}
% \address used twice to have two lines of address
\address{ github.com/ses110 $\mid$ ses110@utexas.edu $\mid$ (305)-213-4130 }
 
\begin{resume}

\section{EDUCATION} {\sl Bachelor of Science}, Computer Science \\
                University of Texas at Austin \hfill August 2014 \\
                {\sl \small Business Foundations }

\section{EXPERIENCE} 
    {\sl Software Developer (Contractor)} \hfill August 2015 - Present \\
    % IBM Bluemix MobileFirst Platform\\
    % Austin, Texas
    { IBM Bluemix MobileFirst Platform } \hfill Austin, Texas \\
    \begin{itemize} \itemsep -2pt
    \item \small Develop open-source Cordova SDKs that allow developers to interact with IBM Bluemix Cloud Services such as MCA (Security, Instrumentation and Analytics) and Push Notifications.
    \item \small Work closely with IBM Bluemix MobileFirst architect to design and develop Cordova SDKs for Android support.
    \item \small Publish open-source SDKs to Node Package Manager (NPM) registry
    \item \small Collaborate in design, documentation and code review discussions
    \item \small Write unit tests using Jasmine framework
    \item \small Participate in full SDLC (Agile Scrum), including meetings, estimations, planning and design sessions.
    \item \small Work in platform as a service (PaaS) environment with an emphasis on continuous delivery.
    \item \small Tools and Technologies: Cordova, Node/NPM, Javascript, Java, Android Studio, Git, Gradle, HTML, CSS, Rational Team Concert (RTC)

% Prepare specifications, design, develop and support mobile applications and prepare documentation per Schwab mobile best practices.
% Assess and optimize designs through review, evaluation tools and analysis to ensure appropriate user experiences for phones and tablets.
% Create and perform unit testing for the spectrum of mobile devices.
% Build mobile apps, support the mobile systems in production and resolve and troubleshoot technical problems.
% Prepare documentation for new development work while maintaining Schwab development standards.

    % [ ] Cordova Applications
    % [ ]    With Ionic / AngularJS
    % [ ] Cordova plugin development
    % [ ]    Define and implement Javascript API
    % [ ]    Integrating with existing Bluemix Android SDKs / Gradle
    % [ ]    Android / Java development for plugin
    % [ ] Github / source code management + Code Reviews / Pull Requests
    % [X] Collaborate with Documentation team and contribute to documentation
    % [X] Contribute to architecture / design collaboration
    % Android dev
    % Hybrid mobile development
    % Javascript frameworks, HTML5, CSS  
    % Strong understanding of web services foundations including RESTful services, JSON
    % Experience working on agile development teams

    % Cordova is a platform for building hybrid applications with JavaScript, CSS, and HTML.

    % Develop Cordova SDK for IBM Push Notifications Service and Mobile Client Access.

    \end{itemize}

    {\sl Mobile Test Automation Engineer } \hfill January - August 2015 \\
    % Mutual Mobile \\
    % Austin, Texas
    { Mutual Mobile } \hfill Austin, Texas \\
    \begin{itemize} \itemsep -2pt
        \item \small Used internal cross-platform automation framework to write test scripts in Python that provide functional test coverage for both iOS and Android apps.
        \item \small Enhanced functionality of the internal cross-platform automation framework such as building from source with Gradle and additional emulator configurations.
        \item \small Contributed to automation tools documentation.
        \item \small Modified Android and iOS apps to reuse common UI components and minimize rewriting test scripts per platform.
    \end{itemize}

    {\sl Android Developer (Intern) } \hfill August - September 2014 \\
    % FDL \\
    % Managua, Nicaragua
    { FDL } \hfill Managua, Nicaragua \\
     \begin{itemize} \itemsep -2pt %reduce space between items
        \item \small Developed Android loan statement app to let employees look up clients' loan statements.
        \item \small Developed backend RESTful web service using Oracle JDeveloper (J2EE) to interact with backend Oracle database and retrieve client data for Android app.
    \end{itemize}

\section{SKILLS \&\\ TOOLS} \small {\sl Experienced with:} Java, Javascript Python, C/C++, HTML/CSS, Linux, PL/SQL \\
                jQuery, Agile (Scrum) \\
                \small {\sl Tools:} Android Studio, Git, Heroku, Django, Bootstrap
                \\\small Native speaker/proficient in Spanish

\section{COURSE-RELATED \& PERSONAL PROJECTS}
    {\sl Mythos}
    \begin{itemize} \itemsep -2pt %reduce space between items
    \item \small Encyclopedia-like Web Application for mythological figures, stories and cultures; implements a RESTful backend API; built with Bootstrap and Django.
    \item \small Modeled backend data and configured PostgreSQL with Heroku, scraped data from Wikipedia to populate our database and implemented search features.
    \end{itemize}

    {\sl DroidyLoops}
    \begin{itemize} \itemsep -2pt
    \item \small Android app built for Mobile App course that lets you sequence sound samples and loop them together to create songs.
    \end{itemize}

\end{resume}
\end{document}
